---
title: "Cheese Slides!"
author: "Diana & Leslie"
output:
  slidy_presentation: 
    highlight: kate
  powerpoint_presentation: default
---

# Cheese: The Good, The Bad, and The Healthy

<!-- Introduction -->

As a couple of cheese lovers, we will try to determine which cheeses people should be eating and which we to stay away from based on the cheeses nutritional content and as they pertain to certain diets.

For example, diets such as...

- Keto diet

- Low calorie diet

- Heart healthy diet

# The Data

We downloaded our dataset from github.

> https://gist.github.com/jalapic/95a72f2c2f5ccfb43e0e0ab35891d745

The cheese dataset contains information for 73 different `type` of cheeses and the following 8 variables for each of them.

- `sat_fat`, saturated fat

- `polysat_fat`, polyunsaturated fat

- `monosat_fat`, monounsaturated fat

- `protein`, protein

- `carb`, carbohydrates

- `chol`, cholesterol

- `fiber`, fiber

- `kcal`, calories.

All the numerical nutritional information will be based on 100g

# Saturated vs. Unsaturated Fats
  
- Saturated Fats

  - They are the unhealthy fats.
  
  - They are usually solid at room temperature and can cause fatty deposits in blood vessels leading to heart disease.
  
  - Mostly found in animal products like meat and dairy  

- Unsaturated Fats

  - They are the healthy fats.
  
  - They are usually liquid at room temperature. And help reduce blood pressure and increase good cholesterol.
  
  - Usually found in plant products, oils, nuts, and fish.
  


```{r echo = FALSE, include=FALSE}
library(tidyverse)
cheese <- read_csv("cheese.csv")
library(plotly)
glimpse(cheese)
library(kableExtra)

```
# Are there any cheeses that align well with a ketogenic diet (high fat, low carb)?

To make this graph, we added a mutated variable `total_fat`, by adding all three fats (`sat_fat, polysat_fat, monosat_fat`) together.

This graph shows that most cheeses can be suitable for a keto diet since carbs are below 13.4g for all...

Except one, gjetost which is at 42.65g.

```{r echo = FALSE}
cheese <- cheese %>% 
  mutate(total_fat = sat_fat + polysat_fat + monosat_fat)
  
keto <- cheese %>% ggplot(aes(total_fat, carb, text = type)) + geom_point(color = "maroon") + labs(title = "Best Cheeses for a Ketogenic Diet")

ggplotly(keto)
```

# Does fiber content vary significantly across cheeses, or is it generally low across all types?

If you didn't know, fiber is the best thing to possibly do for your body when eating. It help with digestion and basically helps regulate blood sugar in your body due to you being able to feel more fuller when eating things that contain fiber. 

From this graph, we are able to determine that mozzarella is the best when it comes to fiber, which fiber at 1.8g. But why? 

When most cheeses have 0 fiber and the few with low fiber are cheeses with some fruit or vegetable in them.

```{r echo = FALSE }
fiber_in_cheese <- cheese %>% 
  ggplot(aes(x = fiber, text = type)) + geom_bar(fill = "seagreen") + labs(title = "How Much Fiber are in Each Cheese")

ggplotly(fiber_in_cheese) %>% layout(showlegend = FALSE)
```

# How does the saturated fat content compare across different cheese types? Are there cheeses with notably higher or lower saturated fat levels?

This table demonstrates which cheeses have low saturated fat which was determined by filtering cheeses that have less than 1 gram of saturated fat in them.

With this table we can see that out of the 73 cheeses, 9 are low saturated fat. So, 88% of cheeses have high saturated fat levels.

As we made this table, we noticed that the top 3 cheeses that have the lowest saturated fat are Mozzarella, Cottage, and Ricotta. 

```{r, echo = FALSE}
cheese %>% select(type, sat_fat) %>% filter(sat_fat < 1) %>% arrange(sat_fat) %>% 
  kbl() %>% kable_styling()
```

# Which cheeses have a profile that might be considered more "heart-healthy" (e.g., lower in saturated fat, higher in unsaturated fat)?

This table is comparing the saturated fat to the total unsaturated fat with a mutated variable `unsat_fat` which is `polysat_fat` and `monosat_fat` added together.

This table also filtered `sat_fat` to be less than 1g because we want cheeses with low saturated fat levels.

We can see that even with low saturated fat levels, the unsaturated fat levels are even lower. So even though these cheeses are not as unhealthy, they are not necessarily more "heart-healthy"


```{r echo = FALSE}
cheese <- cheese %>% 
  mutate(unsat_fat = polysat_fat + monosat_fat)

cheese %>% select(type, sat_fat, unsat_fat) %>% filter(sat_fat < 1) %>% arrange(sat_fat) %>% 
  kbl() %>% kable_styling()

```

```{r echo = FALSE}

# This is easier to see on table

# heart_health <- cheese %>% filter(sat_fat < 1) %>% ggplot(aes(x = sat_fat, y = total_unsat_fat, col =  type)) + geom_point() +labs(title = "Heart Healthy Cheeses to Consider")

# ggplotly(heart_health)
```

# Unsaturated vs Saturated Fat Levels

It can be seen here that as unsaturated fat levels go up so do saturated fat levels.

```{r, echo = FALSE}
fat_levels <- cheese %>% ggplot(aes(x = unsat_fat, y = sat_fat, text = type)) + geom_point(color = "royalblue") + labs(title = "Unsaturated vs Saturated Fat Levels")

ggplotly(fat_levels) %>% layout(showlegend = FALSE)

```


# Are cheeses with higher saturated fat content also higher in total calories?

This graph shows the relationship between sat_fat and calories, as saturated fat increases so does the calories.

For cheese to be a healthy consumption, the calories must be less than 100 per service size, which is about 28g. 

```{r echo = FALSE}
high_risk <- cheese %>% ggplot(aes(x = sat_fat, y = kcal, text = type)) + geom_point(color = "goldenrod") + labs(title = "Worst Cheeses to Consume")

ggplotly(high_risk) %>% layout(showlegend = FALSE)
```

# How does the balance between protein, fat, and carbohydrate content differ between types of cheese? For example, are high-protein cheeses generally lower in carbs?

Here we found that there is no relationship between protein and fat in a cheese.

```{r, echo = FALSE}
psf <- cheese %>% ggplot(aes(x = protein, y = total_fat, text = type)) + geom_point(color = "darkolivegreen4") + labs(title = "Protein V Fat")

ggplotly(psf) %>% layout(showlegend = FALSE)
```

# How does the balance between protein, fat, and carbohydrate content differ between types of cheese? For example, are high-protein cheeses generally lower in carbs?

But for protein and carbs, we found that cheese is generally low in carbs and has no relation to the amount of protein in a cheese.

```{r echo= FALSE}
puc <- cheese %>% ggplot(aes(x = protein, y = carb, text = type)) + geom_point(color = "tomato3") + labs(title = "Protein V Carbs")

ggplotly(puc) %>% layout(showlegend = FALSE)

```
# Can we identify cheese types that are lower in calories, fat, and cholesterol while still providing adequate protein?

In this table, we filtered the cheeses to sat_fat to be less than 1 gram and cholesterol to be less than 20 g and we have seen that low sat_fat also gives us low calories. We decided to arrange by protein to see which cheese will give us the highest protein levels.


```{r, echo = T}
cheese %>% 
  select(type, kcal, sat_fat, chol, protein) %>% 
  filter(sat_fat < 1, chol < 20) %>% 
  arrange(-protein) %>% kbl() %>% kable_styling()
```

# What is the healthiest cheese?

People may have a different opinion on how to determine the healthiest of the cheeses but generally cheeses with low saturated fat and high protein levels tend to be considered the healthiest.

This helped us determine that the following are the best cheeses to eat if you want a healthier diet.

```{r echo=FALSE}
hc <- cheese %>% filter(sat_fat < 1) %>% ggplot(aes(x = sat_fat, y = protein, col =  type)) + geom_point() + labs(title = "Healthiest Cheese")

ggplotly(hc)
```


# Thank You for Listening!
Please feel free to ask questions