---
title: "Cheese Slides!"
author: "Diana & Leslie"
output:
  slidy_presentation: 
    highlight: kate
  powerpoint_presentation: default
---

# Cheese: The Good, The Bad, and The Healthy

<!-- Introduction -->

As a couple of cheese lovers, we will try to determine which cheeses people should be eating and which we to stay away from based on the cheeses nutritional content and as they pertain to certain diets.

For example, diets such as...

- Keto diet

- Low calorie diet

- Heart healthy diet

# The Data

The cheese dataset contains information of 73 different `type` of cheeses and the following 8 variables for each of them.

- `sat_fat`, saturated fat

- `polysat_fat`, polyunsaturated fat

- `monosat_fat`, monounsaturated fat

- `protein`, protein

- `carb`, carbohydrates

- `chol`, cholesterol

- `fiber`, fiber

- `kcal`, calories.

All the numerical nutritional information will be based on 100g

<!-- Our project is based on a cheese dataset, downloaded from Github. -->
<!-- Diana** - I can't find the link anymore -->

```{r echo = FALSE, include=FALSE}
library(tidyverse)
cheese <- read_csv("cheese.csv")
library(plotly)
glimpse(cheese)

```
# Are there any cheeses that align well with a ketogenic diet (high fat, low carb)?

```{r echo = FALSE}

cheese <- cheese %>% 
  mutate(total_fat = sat_fat + polysat_fat + monosat_fat)
  

cheese %>% select(type, total_fat, carb) %>% arrange(-total_fat) %>% head(n = 5) %>% knitr::kable()

```

# How does the saturated fat content compare across different cheese types? Are there cheeses with notably higher or lower saturated fat levels?

This graph demonstrates which cheeses have low saturated fat. As we made this table, we noticed that the top 3 cheeses that have the lowest saturated fat are Moterella, Cottage, and Ricotta. This is determined due to these cheeses having less than 1 gram of saturated fat within them

```{r, echo = FALSE}

cheese %>% select(type, sat_fat) %>% filter(sat_fat < 1) %>% arrange(sat_fat) %>% 
  knitr::kable()

```

# How does cholesterol content vary by cheese type? Which cheeses are lower in cholesterol and might be better suited for people with specific dietary needs?
```{r, echo = FALSE}







```

# Does fiber content vary significantly across cheeses, or is it generally low across all types?

If you didn't know, fiber is the best thing to possibly do for your body when eating. It help with digestion and basically helps regulate blood sugar in your body due to you being able to feel more fuller when eating things that contain fiber. 

From this graph, we are able to determine that mozzarella is the best when it comes to fiber.

```{r echo = FALSE }
fiber_in_cheese <- cheese %>% 
  ggplot(aes(x = fiber, fill = type)) + geom_bar()

ggplotly(fiber_in_cheese) %>% layout(showlegend = FALSE)
```

# Are cheeses with higher saturated fat content also higher in total calories?

For cheese to be a healthy consumption, the calories must be less than 100 when only eating 1 ounce. A high saturated cheese is when an ounce of chees is eater, it gives you more than 3 grams of saturated fat.

```{r echo = FALSE}

high_risk <- cheese %>% filter(sat_fat > 1 & kcal <= 100) %>% ggplot(aes(x = sat_fat, y = kcal, col =  type)) + geom_point()

ggplotly(high_risk)


```

# How does the balance between protein, fat, and carbohydrate content differ between types of cheese? For example, are high-protein cheeses generally lower in carbs?

```{r, echo = FALSE}







```

# Which cheeses have a profile that might be considered more "heart-healthy" (e.g., lower in saturated fat, higher in polyunsaturated fat)?

```{r echo = FALSE}

heart_health <- cheese %>% filter(sat_fat < 1 & polysat_fat <= 1.4) %>% ggplot(aes(x = sat_fat, y = polysat_fat, col =  type)) + geom_point()

ggplotly(heart_health)

```

# Can we identify cheese types that are lower in calories, fat, and cholesterol while still providing adequate protein?


```{r, echo = FALSE, results='asis'}

cheese %>% 
  select(type, kcal, sat_fat, chol, protein) %>% 
  filter(sat_fat < 1.5, chol < 20) %>% 
  arrange(-protein) %>% 
  knitr::kable()

```

# What is the healthiest cheese?

People may have a different opinion on how to determine the healthiest of the cheeses but generally cheeses with low saturated fat and high protein levels tend to be concidered the healthiest.

This helped us determine that the following are the best cheeses to eat if you 
want a healthier diet.

```{r echo=FALSE}


hc <- cheese %>% filter(sat_fat < 1) %>% ggplot(aes(x = sat_fat, y = protein, col =  type)) + geom_point()

ggplotly(hc)

```